---
title: "Data Wrangling Project 2"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```
library(readr)
library(dplyr)
library(tidyr)

# Read the CSV file into a dataframe

titanic_original <- read.csv("~/RProjects/titanic_original.csv")

# Create a new dataframe for cleaning

titanic_clean <- titanic_original

# Find missing values in the embarked column and replace them with S

titanic_clean$embarked[is.na(titanic_clean$embarked)] <- "S"

# Enter the mean of the ages in the age column for missing values in that column

mean_age <- mean(titanic_clean$age, na.rm = TRUE)
titanic_clean$age[is.na(titanic_clean$age)] <- mean_age

# Fill missing values in the boat column with None

titanic_clean$boat[titanic_clean$boat==""]<-NA
titanic_clean$boat <- as.character(titanic_clean$boat)
titanic_clean$boat[is.na(titanic_clean$boat)] <- "None"

# Add a column with a binary indicator of whether or not there is a cabin number.

titanic_clean$cabin[titanic_clean$cabin==""]<-NA
titanic_clean$cabin <- as.character(titanic_clean$cabin)
  
titanic_clean <- titanic_clean %>% 
  mutate(has_cabin_number = ifelse(is.na(cabin),0,1))

write.csv(titanic_clean, file = "titanic_clean.csv")
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
